Capstone Movielens Report

### 2025-10-21 reports/capstone-movielens.site/05.appendix.Rmd
Functions described: get_log2, print_log2, put_log2, get_log3, print_log3, put_log3.

>>>>

#### [get_log2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L45) Function {#func.get_log2}
\

Builds a string from the template passed in the [msg_template](#func.get_log2.args.msg_template) argument using the format values specified by the [arg1](#func.get_log2.args.arg1) and [arg2](#func.get_log2.args.arg2) arguments.

::: { #func.get_log2.Usage .sidebar }
##### Usage
\

```{r eval=FALSE}
get_log2(msg_template, arg1, arg2)
```
:::

::: { #func.get_log2.args .sidebar }
##### Arguments
\

::: { #func.get_log2.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").

::: { #func.get_log2.args.arg1 .sidebar }
  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.get_log2.args.msg_template) argument.

::: { #func.get_log2.args.arg2 .sidebar }
  - **arg2:** The value to replace the format elements represented by the substring `%2` in the message template specified by the [msg_template](#func.get_log2.args.msg_template) argument.

::: { #func.get_log2.details .sidebar }
##### Details
\

This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to format a string from the template using the format value passed in the [msg_template](#func.get_log2.args.msg_template), [arg1](#func.get_log2.args.arg1), and [arg2](#func.get_log2.args.arg2)  arguments, respectively.

::: { #func.get_log2.value .sidebar }
##### Value
\

::: { #func.get_log2.code .sidebar }
##### Source Code
\

The source code of the [get_log2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L45) function is shown below:
```{r eval=FALSE}
get_log2 <- function(msg_template, arg1, arg2) {
  msg_template |> 
    str_replace_all("%1", as.character(arg1)) |>
    str_replace_all("%2", as.character(arg2)) |>
    str_glue()
}
```

::: {.noteblock data-latex=""}
The source code of the [get_log2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L45) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L45) script on _GitHub_.
:::
:::

#### [print_log2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L51) Function {#func.print_log2}
\

Prints a string formed from the template passed in the [msg_template](#func.print_log2.args.msg_template) argument using the format values specified by the [arg1](#func.print_log2.args.arg1) and [arg2](#func.print_log2.args.arg2) arguments.

::: { #func.print_log2.Usage .sidebar }
##### Usage
\

```{r eval=FALSE}
print_log2(msg_template, arg1, arg2)
```
:::

::: { #func.print_log2.args .sidebar }
##### Arguments
\

::: { #func.print_log2.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").

::: { #func.print_log2.args.arg1 .sidebar }
  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.print_log2.args.msg_template) argument.

::: { #func.print_log2.args.arg2 .sidebar }
  - **arg2:** The value to replace the format elements represented by the substring `%2` in the message template specified by the [msg_template](#func.print_log2.args.msg_template) argument.

::: { #func.print_log2.details .sidebar }
##### Details
\

This function internally calls the [base::print](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/print) `R` function to print the string (possibly multiline) produced by the (also called internally) [get_log2](#func.get_log2) function described above.

::: { #func.print_log2.value .sidebar }
##### Value
\

A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [get_log2](#func.get_log2) function described above.

::: { #func.print_log2.code .sidebar }
##### Source Code
\

The source code of the [print_log2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L51) function is shown below:
```{r eval=FALSE}
print_log2 <- function(msg_template, arg1, arg2){
  print(get_log2(msg_template, arg1, arg2))
}
```

::: {.noteblock data-latex=""}
The source code of the [print_log2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L51) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L51) script on _GitHub_.
:::
:::

#### [put_log2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L54) Function {#func.put_log2}
\

Outputs a string to the currently open log (using the [open_logfile](#func.open_logfile) function described above) formed from the template passed in the [msg_template](#func.put_log2.args.msg_template) argument using the format values specified by the [arg1](#func.put_log2.args.arg1) and [arg2](#func.put_log2.args.arg2) arguments.

::: { #func.put_log2.Usage .sidebar }
##### Usage
\

```{r eval=FALSE}
put_log2(msg_template, arg1, arg2)
```
:::

::: { #func.put_log2.args .sidebar }
##### Arguments
\

::: { #func.put_log2.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").

::: { #func.put_log2.args.arg1 .sidebar }
  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.put_log2.args.msg_template) argument.

::: { #func.put_log2.args.arg2 .sidebar }
  - **arg2:** The value to replace the format elements represented by the substring `%2` in the message template specified by the [msg_template](#func.put_log2.args.msg_template) argument.

::: { #func.put_log2.details .sidebar }
##### Details
\

This function internally calls the [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print) `R` function to output the string (possibly multiline) produced by the (also called internally) [get_log2](#func.get_log2) function described above.

The function works similarly to the [print_log2](#func.print_log2) function described above, but unlike the latter, it outputs the information to the currently open log file.

::: { #func.put_log2.value .sidebar }
##### Value
\

A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [get_log2](#func.get_log2) function described above.
:::

::: { #func.put_log2.code .sidebar }
##### Source Code
\

The source code of the [put_log2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L54) function is shown below:
```{r eval=FALSE}
put_log2 <- function(msg_template, arg1, arg2){
  put(get_log2(msg_template, arg1, arg2))
}
```

::: {.noteblock data-latex=""}
The source code of the [put_log2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L54) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L54) script on _GitHub_.
:::
:::

#--------------------------------------

#### [get_log3](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L58) Function {#func.get_log3}
\

Builds a string from the template passed in the [msg_template](#func.get_log3.args.msg_template) argument using the format values specified by the [arg1](#func.get_log3.args.arg1), [arg2](#func.get_log3.args.arg2), and [arg3](#func.get_log3.args.arg3) arguments.

::: { #func.get_log3.Usage .sidebar }
##### Usage
\

```{r eval=FALSE}
get_log3(msg_template, arg1, arg2, arg3)
```
:::

::: { #func.get_log3.args .sidebar }
##### Arguments
\

::: { #func.get_log3.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").

::: { #func.get_log3.args.arg1 .sidebar }
  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.get_log3.args.msg_template) argument.

::: { #func.get_log3.args.arg2 .sidebar }
  - **arg2:** The value to replace the format elements represented by the substring `%2` in the message template specified by the [msg_template](#func.get_log3.args.msg_template) argument.

::: { #func.get_log3.args.arg3 .sidebar }
  - **arg3:** The value to replace the format elements represented by the substring `%3` in the message template specified by the [msg_template](#func.get_log3.args.msg_template) argument.

::: { #func.get_log3.details .sidebar }
##### Details
\

This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to format a string from the template using the format value passed in the [msg_template](#func.get_log3.args.msg_template), [arg1](#func.get_log3.args.arg1), [arg2](#func.get_log3.args.arg2), and [arg3](#func.get_log3.args.arg3)  arguments, respectively.

::: { #func.get_log3.value .sidebar }
##### Value
\

::: { #func.get_log3.code .sidebar }
##### Source Code
\

The source code of the [get_log3](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L58) function is shown below:
```{r eval=FALSE}
get_log3 <- function(msg_template, arg1, arg2, arg3) {
  msg_template |> 
    str_replace_all("%1", as.character(arg1)) |>
    str_replace_all("%2", as.character(arg2)) |>
    str_glue()
}
```

::: {.noteblock data-latex=""}
The source code of the [get_log3](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L58) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L58) script on _GitHub_.
:::
:::

#### [print_log3](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L65) Function {#func.print_log3}
\

Prints a string formed from the template passed in the [msg_template](#func.print_log3.args.msg_template) argument using the format values specified by the [arg1](#func.print_log3.args.arg1), [arg2](#func.print_log3.args.arg2), and [arg3](#func.print_log3.args.arg3) arguments.

::: { #func.print_log3.Usage .sidebar }
##### Usage
\

```{r eval=FALSE}
print_log3(msg_template, arg1, arg2, arg3)
```
:::

::: { #func.print_log3.args .sidebar }
##### Arguments
\

::: { #func.print_log3.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").

::: { #func.print_log3.args.arg1 .sidebar }
  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.print_log3.args.msg_template) argument.

::: { #func.print_log3.args.arg2 .sidebar }
  - **arg2:** The value to replace the format elements represented by the substring `%2` in the message template specified by the [msg_template](#func.print_log3.args.msg_template) argument.

::: { #func.print_log3.args.arg3 .sidebar }
  - **arg3:** The value to replace the format elements represented by the substring `%3` in the message template specified by the [msg_template](#func.print_log3.args.msg_template) argument.

::: { #func.print_log3.details .sidebar }
##### Details
\

This function internally calls the [base::print](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/print) `R` function to print the string (possibly multiline) produced by the (also called internally) [get_log3](#func.get_log3) function described above.

::: { #func.print_log3.value .sidebar }
##### Value
\

A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [get_log3](#func.get_log3) function described above.

::: { #func.print_log3.code .sidebar }
##### Source Code
\

The source code of the [print_log3](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L65) function is shown below:
```{r eval=FALSE}
print_log3 <- function(msg_template, arg1, arg2, arg3){
  print(get_log3(msg_template, arg1, arg2, arg3))
}
```

::: {.noteblock data-latex=""}
The source code of the [print_log3](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L65) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L65) script on _GitHub_.
:::
:::

#### [put_log3](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L68) Function {#func.put_log3}
\

Outputs a string to the currently open log (using the [open_logfile](#func.open_logfile) function described above) formed from the template passed in the [msg_template](#func.put_log3.args.msg_template) argument using the format values specified by the [arg1](#func.put_log3.args.arg1), [arg2](#func.put_log3.args.arg2), and [arg3](#func.put_log3.args.arg3) arguments.

::: { #func.put_log3.Usage .sidebar }
##### Usage
\

```{r eval=FALSE}
put_log3(msg_template, arg1, arg2, arg3)
```
:::

::: { #func.put_log3.args .sidebar }
##### Arguments
\

::: { #func.put_log3.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").

::: { #func.put_log3.args.arg1 .sidebar }
  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.put_log3.args.msg_template) argument.

::: { #func.put_log3.args.arg2 .sidebar }
  - **arg2:** The value to replace the format elements represented by the substring `%2` in the message template specified by the [msg_template](#func.put_log3.args.msg_template) argument.

::: { #func.get_log3.args.arg3 .sidebar }
  - **arg3:** The value to replace the format elements represented by the substring `%3` in the message template specified by the [msg_template](#func.put_log3.args.msg_template) argument.

::: { #func.put_log3.details .sidebar }
##### Details
\

This function internally calls the [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print) `R` function to output the string (possibly multiline) produced by the (also called internally) [get_log3](#func.get_log3) function described above.

The function works similarly to the [print_log3](#func.print_log3) function described above, but unlike the latter, it outputs the information to the currently open log file.

::: { #func.put_log3.value .sidebar }
##### Value
\

A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [get_log3](#func.get_log3) function described above.
:::

::: { #func.put_log3.code .sidebar }
##### Source Code
\

The source code of the [put_log3](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L68) function is shown below:
```{r eval=FALSE}
put_log3 <- function(msg_template, arg1, arg2, arg3){
  put(get_log3(msg_template, arg1, arg2, arg3))
}
```

::: {.noteblock data-latex=""}
The source code of the [put_log3](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L68) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L68) script on _GitHub_.
:::
:::
